\documentclass[10pt, a4paper, bibliography=totocnumbered]{article}
\usepackage[utf8]{inputenc}
\usepackage{parskip}
\usepackage{setspace}
\usepackage{geometry}
\usepackage{ngerman}
\usepackage{multicol}
\usepackage{setspace}
\usepackage[hyphens]{url}
\usepackage[T1]{fontenc}
\usepackage{enumitem}
\usepackage{tikz}
%\usepackage{arev}
\usepackage{newcent} % Schriftart
\usepackage{microtype} % Optimiere Rand und Trennstellen
\usepackage{spverbatim}
\usepackage{graphicx}
\usepackage{tabularx}
%\usepackage[colorlinks=true,linkcolor=blue]{hyperref}
\usepackage[breaklinks,colorlinks=true,allcolors=blue]{hyperref}
\usepackage[square,numbers]{natbib}
\bibliographystyle{plainnat}
\setcitestyle{authoryear,open={},close={}}
\geometry{a4paper,left=2cm, right=2cm, top=2cm,bottom=2cm}
\usepackage{gb4e}
\begin{document}
\setstretch{1,5} % Ab hier: 1.5er Zeilenabstand
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
  \LARGE{\textbf{Cancellation of the GNUnet e.V. --- p$\equiv$p foundation Agreement\\
      on Shared-Ownership of the GNUnet code}}\\
\end{center}
\normalsize
\section*{Preamble}
In 2016 GNUnet e.V. and p$\equiv$p foundation created an agreement on
shared-ownership of the GNUnet code to foster mutual collaboration
and enable p$\equiv$p to use the GNUnet code in its products.

However, the collaboration never became fruitful and to the best of
our knowledge p$\equiv$p has never started to use GNUnet in its
project.  Instead, there have been some problems between the members
of the different projects in recent years. At the GNUnet e.V. annual
meeting on December 4th 2022 the members discussed the situation and
tasked the board to disolve the agreement as per the termination
clause.

\section*{Termination clause}

Either party can cancel this agreement at any time in the future.
At that point, each party will hold copyright to the GNUnet code
and will be able to continue to evolve the respective codebase
separately. However, the licensing constraints imposed by this
agreement will continue to bind p$\equiv$p foundation indefinitively.

\section*{Invocation}

By this message, GNUnet e.V. invokes the termination clause
quoted above effective immediately, terminating the copyright
sharing agreement with p$\equiv$p foundation.

\section*{Signatures}
\begin{tabularx}{\textwidth}{ XXXX }
GNUnet e.V. & & & \\
& & &\\
& & &\\
\dots{}\dots{}\dots{}\dots{}\dots{}\dots{}\dots{}\dots{}\dots{}&&&
\\
& & &\\
& & &\\
\dots{}\dots{}\dots{}\dots{}\dots{}\dots{}\dots{}\dots{}\dots{}&&&
\\
& & &\\
Date:~~\dots{}\dots{}\dots{}\dots{} & & &\\
\end{tabularx}
%\bibliographystyle{plainnat}
%\begin{flushleft}
%\footnotesize
%\bibliography{ref}
%\normalsize
%\end{flushleft}
\end{document}
